### 2021-03-09 results/draft.tex
wrote the paragraph of joint model

\ \ \ \ \ \ \ \ \ \
Accurate species identification of fish eggs and larvae is essential for elucidating the ecology of the early life--history of fish, including the location and timing of fish spawning, hatching, and migration (Ko et al., 2013). Such information can improve the inference and forecasting of fish population size. Morphological characteristics used for species identification have traditionally been the size and oil globules of eggs, and the body shape, pigmentation, and meristic count of larvae (e.g., Matarese and Sandknop, 1984; Ko et al., 2013). However, species identification based on these morphological characteristics leads to species misidentification because these morphological characteristics are likely to overlap among species in early life--history (e.g., Victor et al., 2009; Ko et al., 2013). For example, when we use size of eggs as a morphological measure, we often classify eggs by whether their diameters are greater than or less than a predetermined value. However, because distributions of diameters are likely to overlap among species, some eggs may be erroneously classified as different species. In addition, morphological characteristics can change during developments, so that individuals of the same species at different development stages can be misidentified as a different species (Ko et al., 2013).

\ \ \ \ \ \ \ \ \ \
Spotted mackerel \textit{Scomber australasicus} and chub mackerel \textit{Scomber japonicus} are small pelagic fish that are widely distributed in the western North Pacific (ca. $\textrm{120}-\textrm{150}^{\circ}$E, Fig. 1; Watanabe and Yatsu, 2006). These species spawn in waters near the Kuroshio Current from winter to summer (e.g., Watanabe, 1970; Watanabe et al., 1999; Watanabe and Yatsu, 2006), after which the adults and their offspring are transported to their feeding ground by the Kuroshio Current (e.g., Watanabe and Nishida, 2002). Because Nishida (2001) suggested that egg diameter differs between the two species, species identification based on egg diameter has been conducted routinely since 2005; eggs smaller than 1.1 mm in diameter were classified as chub mackerel and vice versa. These eggs, which were identified according to this basis, have been used as the indices of the spawning stock biomass of spotted mackerel and chub mackerel for stock assessment. However, the recent egg density of spotted mackerel was considerably high although stock biomass and spawning stock biomass has been low (Yukami et al., 2019). This considerable increase in the egg density of spotted mackerel is likely the result of overestimation because the difference in egg diameter has become ambiguous according to the increase in the egg density of chub mackerel and overlapping the distributions of egg diameters in the two species (Yukami et al., 2019). That is, the boundary between the left tail of the distribution of egg diameters of spotted mackerel and the right tail of the distribution of egg diameters of chub mackerel is clear when egg density of chub mackerel is low. In contrast, this boundary becomes unclear when egg density of chub mackerel increases because the whole of the distribution of egg diameters of chub mackerel becomes large and includes the distribution of egg diameters of spotted mackerel (i.e., the distributions of egg diameters of two species are overlapped). Owing to the possibility of overestimation, it is problematic to use a yearly trend simply estimated from the egg density data as a spawning stock biomass index for stock assessment, which could lead to sources of bias in stock assessment.

>>>>

\ \ \ \ \ \ \ \ \ \
One step towards overcoming these uncertinties is a understanding of the "ecology of eDNA":  (Barnes \& Turner 2016). Previous studies

\ \ \ \ \ \ \ \ \ \
Integrated species distribution models are now common spatial model to predict spatial pattern of species (Issac et al. 2020).
The model use the different type of data with strengths and weaknesses, such as scientific survey data which is restricted spatially and quantitatively and opportunistic citizen data wihch is widely collected and abundant, and combine in a single model (Isaac et al. 2020; Miller et al. 2019).

The models combine the different type of data with strengths and weaknesses in a single model ().
For example, scientific survey data are high quality but less abundant due to restriction of spatially costly while opportunistic data such as citizen data are widely collected and abundant but may be low quality due to not using consistent field methods.
Combining both types of data can capitalize on the strengths of each data and perform better prediction than models when we use single data (Pacifici et al. 2017; Miller et al. 2019).
